Screen Time Review of Reviews Summary

### 2021-07-28 index.Rmd
Add target for reading study level data
Meta analysis (#6)
* Add target for reading study level data

* Move packages into targets format.

* Convert effect sizes.

* Meta-analyse individual study data

* Add some temporary graphs to compare effect sizes

```{r, load-targets}
tar_load(prisma)
tar_load(effects_clean)
tar_load(reviews_table)
tar_load(plots)
```

@@

@@

## Project Structure
```{r message=FALSE, warning=FALSE}
tar_visnetwork()
```

>>>>

```{r, load-targets}
tar_load(prisma)
tar_load(effects_clean)
tar_load(reviews_table)
tar_load(plots)
tar_load(studies_results)
tar_load(comparison_plots)
```

@@

# Individual Studies

Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes.

```{r, fig.cap="Forest Plot for Health Behaviour Outcomes", fig.width=12, fig.height=10}
comparison_plots$`health behaviour`
```

```{r, fig.cap="Forest Plot for Physical Health Outcomes", fig.width=12, fig.height=10}
comparison_plots$`physical health`
```

```{r, fig.cap="Forest Plot for Psychology Outcomes", fig.width=12, fig.height=10}
comparison_plots$psychology
```

```{r, fig.cap="Forest Plot for Education Outcomes", fig.width=12, fig.height=10}
comparison_plots$education
```

@@

## Project Structure
```{r message=FALSE, warning=FALSE}
tar_visnetwork(targets_only = TRUE)
```
